Management induced changes of soil organic carbon on global croplands

### 2020-12-14 ResultNotebooks/results_SOCmaps.Rmd
nce pdf, update bib + type in maps

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression(paste('croplands \u0394SOC in tons of carbon per hectare')), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("< -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

>>>>

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression(paste('cropland \u0394SOC in tons of carbon per hectare')), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("< -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )

### 2020-12-14 SOCbudgetPaper/SOCbudget.tex
nce pdf, update bib + type in maps

\% latex table generated in R 3.6.3 by xtable 1.8-4 package
\% Mon Dec 14 03:22:10 2020

\begin{table}[ht]
\centering
\begin{tabular}{rlllllll}
  \hline
 & Source & Input & Year & tropical moist & tropical dry & temperate dry & temperate moist \\ 
  \hline
1 & IPCC2006 & low & invariant & 0.44 & 0.55--0.61 & 0.74 & 0.66 \\ 
  2 & IPCC2006 & medium & invariant & 0.48 & 0.58--0.64 & 0.80 & 0.69 \\ 
  3 & IPCC2006 & high & invariant & 0.53 & 0.60--0.67 & 0.83 & 0.77 \\ 
  4 & IPCC2019 & low & invariant & 0.76 & 0.87 & 0.70--0.71 & 0.66--0.67 \\ 
  5 & IPCC2019 & medium & invariant & 0.83 & 0.92 & 0.76--0.77 & 0.69--0.70 \\ 
  6 & IPCC2019 & high & invariant & 0.92 & 0.96 & 0.79--0.80 & 0.77--0.78 \\ 
  7 & This Study & hist & 1990 & 0.57 & 0.61 & 0.78 & 0.76 \\ 
  8 & This Study & hist & 2010 & 0.64 & 0.68 & 0.83 & 0.83 \\ 
   \hline
\end{tabular}
\caption{$F^{\mathrm{SCF}}$ in comparison to IPCC Tier 1 default factors: Stock change factors are in good agreement with the default values of the IPCC in general. For the tropical regions the assumptions changed notablly from the guidelines in 2006 to the update in 2019. leaving our results in very good agreement with the old default assumptions. Default assumption are given under the assumption of medium input systems, which, considering the yield gap in mainly developing regions in the tropics, might be an overestimation and decrease $F^{\mathrm{SCF}}$ by additional 5-8 percent. Also modelled $F^{SOC}$ have increased for all climates over time.} 
\end{table}

@@

\codedataavailability{We compile calculations as open-source R packages available at github.com/pik-piam/mrcommons \cite{bodirsky_mrcommons_2020} for the management related functions, github.com/pik-piam/mrsoil \cite{karstens_mrcommons_2020} for soil dynamic related functions and github.com/pik-piam/mrvalidation \cite{bodirsky_mrvalidation_2020} for validation data. All libraries are based on the MADRaT package at github.com/pik-piam/madrat \cite{dietrich_madrat_2020}, a framework which aims to improve reproducibility and transparency in data processing. Model results are accessable under (zenode\_link). Software code for paper and result prepartion can be found under www.github.com/k4rst3ns/historicalsocmanegement.} %% use this section when having data sets and software code available

>>>>

\% latex table generated in R 3.6.3 by xtable 1.8-4 package
\% Mon Dec 14 03:39:00 2020

\begin{table}[ht]
\centering
\begin{tabular}{rlllllll}
  \hline
 & Source & Input & Year & tropical moist & tropical dry & temperate dry & temperate moist \\ 
  \hline
1 & IPCC2006 & low & invariant & 0.44 & 0.55--0.61 & 0.74 & 0.66 \\ 
  2 & IPCC2006 & medium & invariant & 0.48 & 0.58--0.64 & 0.80 & 0.69 \\ 
  3 & IPCC2006 & high & invariant & 0.53 & 0.60--0.67 & 0.83 & 0.77 \\ 
  4 & IPCC2019 & low & invariant & 0.76 & 0.87 & 0.70--0.71 & 0.66--0.67 \\ 
  5 & IPCC2019 & medium & invariant & 0.83 & 0.92 & 0.76--0.77 & 0.69--0.70 \\ 
  6 & IPCC2019 & high & invariant & 0.92 & 0.96 & 0.79--0.80 & 0.77--0.78 \\ 
  7 & This Study & hist & 1990 & 0.57 & 0.61 & 0.78 & 0.76 \\ 
  8 & This Study & hist & 2010 & 0.64 & 0.68 & 0.83 & 0.83 \\ 
   \hline
\end{tabular}
\caption{$F^{\mathrm{SCF}}$ in comparison to IPCC Tier 1 default factors: Stock change factors are in good agreement with the default values of the IPCC in general. For the tropical regions the assumptions changed notablly from the guidelines in 2006 to the update in 2019. leaving our results in very good agreement with the old default assumptions. Default assumption are given under the assumption of medium input systems, which, considering the yield gap in mainly developing regions in the tropics, might be an overestimation and decrease $F^{\mathrm{SCF}}$ by additional 5-8 percent. Also modelled $F^{SOC}$ have increased for all climates over time.} 
\label{tab:SCFglo}
\end{table}

@@

\codedataavailability{We compile calculations as open-source R packages available at github.com/pik-piam/mrcommons \cite{bodirsky_mrcommons_2020} for the management related functions, github.com/pik-piam/mrsoil \cite{karstens_mrsoil_2020} for soil dynamic related functions and github.com/pik-piam/mrvalidation \cite{bodirsky_mrvalidation_2020} for validation data. All libraries are based on the MADRaT package at github.com/pik-piam/madrat \cite{dietrich_madrat_2020}, a framework which aims to improve reproducibility and transparency in data processing. Model results are accessable under (zenode\_link). Software code for paper and result prepartion can be found under www.github.com/k4rst3ns/historicalsocmanegement.} %% use this section when having data sets and software code available

### 2020-12-14 SOCbudgetPaper/discussion.Rmd
nce pdf, update bib + type in maps

```{r SCFglo, echo=FALSE, results = 'asis'}
table <- readRDS("../ResultNotebooks/Output/SFC_comparison.rds")
library(xtable)
print(xtable(table$comparison_table, digit=2, comment=FALSE, 
              caption="$F^{\\mathrm{SCF}}$ in comparison to IPCC Tier 1 default factors: Stock change factors are in good agreement with the default values of the IPCC in general. For the tropical regions the assumptions changed notablly from the guidelines in 2006 to the update in 2019. leaving our results in very good agreement with the old default assumptions. Default assumption are given under the assumption of medium input systems, which, considering the yield gap in mainly developing regions in the tropics, might be an overestimation and decrease $F^{\\mathrm{SCF}}$ by additional 5-8 percent. Also modelled $F^{SOC}$ have increased for all climates over time."))
```

>>>>

```{r SCFglo, echo=FALSE, results = 'asis'}
table <- readRDS("../ResultNotebooks/Output/SFC_comparison.rds")
library(xtable)
print(xtable(table$comparison_table, digit=2, comment=FALSE, label="tab:SCFglo", 
              caption="$F^{\\mathrm{SCF}}$ in comparison to IPCC Tier 1 default factors: Stock change factors are in good agreement with the default values of the IPCC in general. For the tropical regions the assumptions changed notablly from the guidelines in 2006 to the update in 2019. leaving our results in very good agreement with the old default assumptions. Default assumption are given under the assumption of medium input systems, which, considering the yield gap in mainly developing regions in the tropics, might be an overestimation and decrease $F^{\\mathrm{SCF}}$ by additional 5-8 percent. Also modelled $F^{SOC}$ have increased for all climates over time."))
```
